MSDS_6372_Project2

### 2022-07-25 MSDS_6372_Project2.Rmd
commit

################ Misclassification rate train ######################################
cross.table.interaction.train = table(class.LogReg.Interaction.train,train$fracture)
MCR_interaction.train = (cross.table.interaction.train[2]+cross.table.interaction.train[3])/dim(train)[1]
print(paste('Misclassification Rate for stepwise selection on training set: ', MCR_interaction.train))
```

>>>>

################ Misclassification rate train ######################################
cross.table.interaction.train = table(class.LogReg.Interaction.train,train$fracture)
MCR_interaction.train = (cross.table.interaction.train[2]+cross.table.interaction.train[3])/dim(train)[1]
print(paste('Misclassification Rate for stepwise selection on training set: ', MCR_interaction.train))
# to be worked on
```
